### 2022-08-25 manuscript.Rmd
Remove non-breaking spaces

Second, there is an alternative explanation specifically for the effects observed in the insight phase, when the objects were presented together with matching or non-matching keywords.
Namely, the early difference in the N170 component might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the naive condition.
In this condition, objects were presented with non-matching keywords that led participants to indicate that they did not understand what kind of object they were viewing.
These non-matching keywords might have primed participants to expect a certain set of visual features that did actually not come true once the actual object was displayed, potentially provoking a fast and strong brain response within the first 200 ms.
However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the naive condition.
For this control analysis, we again used the semantically informed condition as defined above, but contrasted it against a different control condition.
Namely, we used those objects that were presented with matching keywords (as in the semantically informed condition) but for which participants failed to capitalize on the keywords and instead indicated that they still did not know what kind of object they were viewing (a kind of "failed insight").
This was the case for an average of `r mean(objects_per_condition$Exclude_informed)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
Contrasting the semantically informed condition and the failed insight conditions, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$~=~`r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N170" & phase == "Insight")$df`)~=~`r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$~`r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
Likewise, the reduction of the N400 could also be replicated in this control analysis, $b$~=~`r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`)~=~`r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$~`r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as did the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by the semantic information.

>>>>

Second, there is an alternative explanation specifically for the effects observed in the insight phase, when the objects were presented together with matching or non-matching keywords.
Namely, the early difference in the N170 component might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the naive condition.
In this condition, objects were presented with non-matching keywords that led participants to indicate that they did not understand what kind of object they were viewing.
These non-matching keywords might have primed participants to expect a certain set of visual features that did actually not come true once the actual object was displayed, potentially provoking a fast and strong brain response within the first 200 ms.
However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the naive condition.
For this control analysis, we again used the semantically informed condition as defined above, but contrasted it against a different control condition.
Namely, we used those objects that were presented with matching keywords (as in the semantically informed condition) but for which participants failed to capitalize on the keywords and instead indicated that they still did not know what kind of object they were viewing (a kind of "failed insight").
This was the case for an average of `r mean(objects_per_condition$Exclude_informed)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
Contrasting the semantically informed condition and the failed insight conditions, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
Likewise, the reduction of the N400 could also be replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as did the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by the semantic information.
